Mahotas: Open source software for scriptable computer vision

### 2013-04-26 paper.tex
ENH Replace milk by scipy.cluster.vq
This is a more natural dependency

We start by importing the necessary packages, including numpy and mahotas. We
also use \textit{milk}, to demonstrate how the mahotas output can integrate
with a machine learning package.

\begin{python}
import numpy as np
import mahotas
from mahotas.features import surf
import milk
\end{python}

@@

Using milk, we cluster the descriptors into five groups:

\begin{python}
values, _ = milk.kmeans(descrs, 5)
\end{python}

Finally, we can show the points in different colours.
\begin{python}
colors = np.array(
    [ 255,  25,   1],
    [203,  77,  37],
    [151, 129,  56],
    [ 99, 181,  52],
    [ 47, 233,   5]])
f2 = surf.show_surf(f, spoints[:64], values, colors)
\end{python}

>>>>

We start by importing the necessary packages, including numpy and mahotas. We
also use \textit{scipy.cluster}, to demonstrate how the mahotas output can integrate
with a machine learning package.

\begin{python}
import numpy as np
import mahotas
from mahotas.features import surf
from scipy.cluster import vq
\end{python}

@@

Using \code{scipy.cluster.vq}, we cluster the descriptors into five groups. The
function \code{kmeans2} returns two values: the centroids, which we ignore; and
the cluster ids, which we will use below to assign colours:
\begin{python}
_,cids = vq.kmeans2(vq.whiten(descrs), 5)
\end{python}

Finally, we can show the points in different colours.
\begin{python}
colors = np.array([
    [ 255,  25,   1],
    [203,  77,  37],
    [151, 129,  56],
    [ 99, 181,  52],
    [ 47, 233,   5]])
f2 = surf.show_surf(f, spoints[:64], cids, colors)
\end{python}
